Results visualization across sites

### 2021-12-15 metanalysis_visualization/visualization.Rmd
update pvalue computation
adding the adapted code to incorporate new site results

```{r}
ratios_patients_with_without_psy_all %>%
  filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot( aes(x=time_p, y=percentage, 
              group = siteid, color = siteid))+
  geom_point( aes(shape=siteid, color=siteid) )+
    geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    theme(
      legend.position="bottom",
      plot.title = element_text(size=11)
    ) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
    ggtitle("Percentage: patients with psychiatric conditions / total number of patients") +
    xlab("period (months)")
```

@@

```{r}
names_site_id <- unique(patient_count_psy_period_psy_all$siteid)

@@

@@

### Summary of the codes used per site 
```{r}
mental_codes_qc_output_all <- mental_codes_qc_output_all %>%
    mutate( concept_code = gsub("[.]", "", concept_code ) ) %>%
  unique()

@@

### Estimate number of ICD codes per site and disorder group
Represent this in 16 pannels, if we put all together, due to the different scales we will not be able to really see the differences between results. 
```{r}
numberOfCodesPerDisorderGroup <- mental_codes_qc_output_all %>%
  group_by( disorder_group, siteid ) %>%
  mutate( icd_codes_count = n( )) %>%
  select( disorder_group, siteid, icd_codes_count ) %>%
  unique()

>>>>

```{r}
### add CHOP 
ratios_patients_with_without_psy_chop <- read.delim ( file = "/Users/alba/Desktop/ratios_patients_with_without_psy_chop.txt")

ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy_chop)

ratios_patients_with_without_psy_all %>%
  filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot( aes(x=time_p, y=percentage, 
              group = siteid, color = siteid))+
  geom_point( aes(shape=siteid, color=siteid) )+
    geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    theme(
      legend.position="bottom",
      plot.title = element_text(size=11)
    ) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
    ggtitle("Percentage: patients with psychiatric conditions / total number of patients") +
    xlab("period (months)")
```

@@

```{r}

@@

names_site_id <- unique(df_coefficients_boot$siteid)

@@

### Summary of the codes used per site 
```{r, eval=FALSE}
mental_codes_qc_output_all <- mental_codes_qc_output_all %>%
    mutate( concept_code = gsub("[.]", "", concept_code ) ) %>%
  unique()

@@

### Estimate number of ICD codes per site and disorder group
Represent this in 16 pannels, if we put all together, due to the different scales we will not be able to really see the differences between results. 
```{r, eval=FALSE}
numberOfCodesPerDisorderGroup <- mental_codes_qc_output_all %>%
  group_by( disorder_group, siteid ) %>%
  mutate( icd_codes_count = n( )) %>%
  select( disorder_group, siteid, icd_codes_count ) %>%
  unique()
